Orientation Control System: Enhancing Aerial Maneuvers \\ for Quadruped Robots

### 2022-11-16 humanoids22roscia.tex
typos

Quadrupedal animals, like cats, can rearrange the tail and trunk to correct the orientation during a fall \cite{kane1969dynamical}.
% Tail
Many works in the field of robotics used an additional link as a tail, like in \cite{chu2019null} and \cite{wenger2016frontal}.
This link rotates around an axis that does not pass through the robot \gls{com}: the distances between the axis of rotation and the \gls{com} of both trunk and tail result in a large effect on the total angular momentum even with a small tail mass.
However, the placement of the additional link makes the resulting robot asymmetric. Moreover, due to its limited range of motion, a tail can be used only for a single jump, not for a repeated sequence~\cite{johnson2012tail}.
% Legs reconfig
It is possible to obtain a similar result by creating repetitive circular motions with the feet, like in \cite{hoffman2021exploiting} and \cite{kurtz2021mini}. In the latter work, the authors proposed special heavy boots for Mini Cheetah and used a neural network to calculate online joint trajectories. However, this solution unnecessarily increases the inertia of the legs, complicating the locomotion problem, which can no longer rely on the massless leg assumption. %\annotation{trova un modo per dire che questa complicazione è data dalla massless assumption che non è più valida} 
% Gyros
Another option is to use a \gls{cmg}.
It consists of a wheel, spinning at a constant angular velocity inside two or three actuated gimbals.
Tilting the wheel's axis of rotation generates the gyroscopic torque.
This system is widespread in spacecrafts reorientation \cite{yoon2002spacecraft}, but less frequently exploited in robot locomotion, either wheeled \cite{brown1996single} or legged \cite{mikhalkov2021gyrubot}.
The \gls{cmg} presents interesting capabilities, but the presence of a pan-tilt unit to drive the gyroscope makes it impractical to mount it on a small, lightweight robot.

@@

\subsection{Inertia Selection}
Once the desired inertia $I_f$ is chosen, according to the 2-D Elroy's Beanie model, it is used to realize the 3-D \gls{ocs} (Fig. \ref{fig:flywheel}). 
\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{figures/flywheel_opaque.png}
	\caption{\small The final design of the flywheel, shown together with its inertia principal axes. Here, $h$ is the wheel thickness, $r$ is the inner radius of the wheel and $R$ is the outer one.}
	\label{fig:flywheel}
\end{figure}
We decided to design the flywheels in the shape of hollow cylinders. This shape increases the inertia by locating the mass far away from the rotation axis. The inertia tensor expressed in its principal axes, $\bm{I}_f = \mathrm{diag}\left\{ I_{f, xx}, \, I_{f, yy}, \, I_{f, zz}  \right\}$, depends on the cylinders inner and outer radii, $r$ and $R$, its height $h$ and the material density $\rho$:
\begin{equation}
\begin{split}
I_{f, xx} = I_{f, yy} &= \frac{1}{12}\pi \rho h \left(3\left(R^4 - r^4\right) + h^2\left(R^2 - r^2\right)\right) \\
I_{f, zz} &= \frac{1}{2}\pi \rho h \left(R^4 - r^4\right)
\end{split}
\end{equation}
Notice that in the Elroy's Beanie model, there is a single body that models the complete \gls{ocs}. The inertia introduced in the Elroy's Beanie model has to be split between the two flywheels: $I_{f, zz} = I_f/\left(2\cos(\alpha)\right)$. 
The parameters $R$ and $h$ can be set to have a compact \gls{ocs} and $\rho$ depends on the chosen material, that is stainless steel in our case. The inner radius $r$ can be adjusted to obtain the desired inertia. Spokes with negligible mass connect the wheel to the motor shaft. All the parameters are reported in Table \ref{tab:dim_fw}, together with the selected inertia and mass of a single flywheel.
\begin{table}
	\centering
	\caption{\small Size and dynamic parameters of a single flywheel}
	\begin{tabular}{ccc}
		Parameter & Value & Unit \\
		\hline
		\hline
		$r$ & $2.20\cdot 10^{-2}$ & $\mathrm{m}$ \\
		$R$ & $3.00\cdot 10^{-2}$ & $\mathrm{m}$ \\
		$h$   & $1.02\cdot 10^{-2}$ & $\mathrm{m}$ \\
		$\rho$   & $7.860 \cdot 10^{3}$ & $\mathrm{kg/m^3}$ \\
		$m$   & $1.02\cdot 10^{-1}$ & $\mathrm{kg}$ \\
		$I_{xx}, I_{yy}$   & $3.64 \cdot 10^{-5}$ & $\mathrm{kg \cdot m^2}$ \\
		$I_{zz}$   & $7.11 \cdot 10^{-5}$ & $ \mathrm{kg \cdot m^2}$ \\
	\end{tabular}
	\label{tab:dim_fw}
\end{table}

>>>>

Quadrupedal animals, like cats, can rearrange tail and trunk to correct the orientation during a fall \cite{kane1969dynamical}.
% Tail
Many works in the field of robotics used an additional link as a tail, like in \cite{chu2019null} and \cite{wenger2016frontal}.
This link rotates around an axis that does not pass through the robot \gls{com}: the distances between the axis of rotation and the \gls{com} of both trunk and tail result in a large effect on the total inertia even with a small tail mass.
However, the placement of the additional link makes the resulting robot asymmetric. Moreover, due to its limited range of motion, a tail can be used only for a single jump, not for a repeated sequence~\cite{johnson2012tail}.
% Legs reconfig
It is possible to obtain a similar result by creating repetitive circular motions with the feet, like in \cite{hoffman2021exploiting} and \cite{kurtz2021mini}. In the latter work, the authors proposed special heavy boots for Mini Cheetah and used a neural network to calculate online joint trajectories. However, this solution unnecessarily increases the inertia of the legs, complicating the locomotion problem, which can no longer rely on the massless leg assumption. %\annotation{trova un modo per dire che questa complicazione è data dalla massless assumption che non è più valida} 
% Gyros
Another option is to use a \gls{cmg}.
It consists of a wheel, spinning at a constant angular velocity inside two or three actuated gimbals.
Tilting the wheel's axis of rotation generates the gyroscopic torque.
This system is widespread in spacecrafts reorientation \cite{yoon2002spacecraft}, but less frequently exploited in robot locomotion, either wheeled \cite{brown1996single} or legged \cite{mikhalkov2021gyrubot}.
The \gls{cmg} presents interesting capabilities, but the presence of a pan-tilt unit to drive the gyroscope makes it impractical to mount it on a small, lightweight robot.

@@

\subsection{Inertia Selection}
Once the desired inertia $I_f$ is chosen, according to the 2D Elroy's Beanie model, it is used to realize the 3D \gls{ocs} (Fig. \ref{fig:flywheel}). 
\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{figures/flywheel_opaque.png}
	\caption{\small The final design of the flywheel, shown together with its inertia principal axes. Here, $h$ is the wheel thickness, $r$ is the inner radius of the wheel and $R$ is the outer one.}
	\label{fig:flywheel}
\end{figure}
We decided to design the flywheels in the shape of hollow cylinders. This shape increases the inertia by locating the mass far away from the rotation axis. The inertia tensor expressed in its principal axes, $\bm{I}_f = \mathrm{diag}\left\{ I_{f, xx}, \, I_{f, yy}, \, I_{f, zz}  \right\}$, depends on the cylinders inner and outer radii, $r$ and $R$, its height $h$ and the material density $\rho$:
\begin{equation}
\begin{split}
I_{f, xx} = I_{f, yy} &= \frac{1}{12}\pi \rho h \left(3\left(R^4 - r^4\right) + h^2\left(R^2 - r^2\right)\right) \\
I_{f, zz} &= \frac{1}{2}\pi \rho h \left(R^4 - r^4\right)
\end{split}
\end{equation}
Notice that in the Elroy's Beanie model, there is a single body that models the complete \gls{ocs}. The inertia introduced in the Elroy's Beanie model has to be split between the two flywheels: $I_{f, zz} = I_f/\left(2\cos(\alpha)\right)$. 
The parameters $R$ and $h$ can be set to have a compact \gls{ocs} and $\rho$ depends on the chosen material, that is stainless steel in our case. The inner radius $r$ can be adjusted to obtain the desired inertia. Spokes with negligible mass connect the wheel to the motor shaft. All the parameters are reported in Table \ref{tab:dim_fw}, together with the selected inertia and mass of a single flywheel.
\begin{table}
	\centering
	\caption{\small Size and dynamic parameters of a single flywheel}
	\begin{tabular}{ccc}
		Parameter & Value & Unit \\
		\hline
		\hline
		$r$ & $2.20\cdot 10^{-2}$ & $\mathrm{m}$ \\
		$R$ & $3.00\cdot 10^{-2}$ & $\mathrm{m}$ \\
		$h$   & $1.02\cdot 10^{-2}$ & $\mathrm{m}$ \\
		$\rho$   & $7.860 \cdot 10^{3}$ & $\mathrm{kg/m^3}$ \\
		$m$   & $1.02\cdot 10^{-1}$ & $\mathrm{kg}$ \\
		$I_{xx}, I_{yy}$   & $3.64 \cdot 10^{-5}$ & $\mathrm{kg \cdot m^2}$ \\
		$I_{zz}$   & $7.11 \cdot 10^{-5}$ & $ \mathrm{kg \cdot m^2}$ \\
	\end{tabular}
	\label{tab:dim_fw}
\end{table}
